Dissecting Neural Style Transfer

### 2019-05-27 paper/paper.tex
1

Now we wonder, could we achieve similar results with other ways to compare 
distribution of features?
One approach would be to consider the \emph{comparison} as a whole to find 
substitutes. 
For example, minimising the mean square errors between two Gram matrices could be seen as 
a special case for minimising a Maximum Mean Discrepancy, which means other Maximum Mean Discrepacies
could be used \cite{MMD}.
For us, it seemed more natural to consider substitutes for the process itself of 
transforming a feature map into a Gram matrix. 
That is, we will consider other
mappings that remove the spatial information or where features are in a feature map but retain
the distribution of features, like a histogram.
Such functions need to be differentiable as well, otherwise they would render the 
optimisation infeasible.

@@

@@

>>>>

Now we wonder, could we achieve similar results with other ways to compare 
distribution of features?
One approach would be to consider the \emph{comparison} as a whole to find 
substitutes. 
For example, minimising the mean square errors between two Gram matrices could be seen as 
a special case for minimising a Maximum Mean Discrepancy (MMD), which means other Maximum Mean Discrepacies
could be used \cite{MMD}.

[[[[Maybe Describe MMD here]]]]

For us, it seemed more natural to consider substitutes for the process itself of 
transforming a feature map into a Gram matrix. 
That is, we will consider other
mappings that remove the spatial information or where features are in a feature map but retain
the distribution of features, like a histogram.
Such functions need to be differentiable as well, otherwise they would render the 
optimisation infeasible.

@@

To find more dislocators, let us consider \emph{how to describe a distribution} in general?
The obvious answer is then statistics, like mean, standard deviation,

@@

\subsection{Reproducing the original result}
